Forecasting the 2024 Election: Trump Dominates the South, Harris Leads in the Midwest

### 2024-10-20 paper/paper.qmd
committing text changes to measurement in data section

Placeholder - The measurement of voter support in our dataset is derived from polling data, which serves as a representation of public sentiment during the 2024 U.S. Presidential Election. Each entry in the dataset corresponds to a poll conducted by various polling organizations, capturing the percentage of respondents who express support for Donald Trump or Kamala Harris. To ensure the quality of the data, only polls from reputable pollsters with a numeric grade of 3 or higher and transparency scores above 6 were included. These polls measure voter preferences through structured survey questions, and the results are aggregated to create state-level averages for each candidate. The dataset thus transforms individual polling responses into a broader measurement of voter sentiment, reflecting the competitive dynamics between Trump and Harris across different states.

>>>>

The measurement of voter support in the dataset is derived from raw polling data obtained from the Project 538 online database, which serves as a representation of potential election results for the 2024 U.S. Presidential Election. Each entry in the dataset corresponds to a poll conducted by each pollster, capturing the percentage of respondents who express support for Donald Trump or Kamala Harris. Each pollster has their approach of sampling respondents as well as their methodology of approaching respondents, which affects each pollster’s numeric grades and transparency scores.  Therefore, to ensure the quality of the data, only polls from reputable pollsters with a numeric grade of 3 or higher and transparency scores above 6 were used for our paper. These polls measure voter preferences through structured survey questions, and the results are aggregated to create state-level averages for each candidate. The dataset thus transforms general voter sentiment into individual data points that reflect the competitive dynamics between Trump and Harris across different states.
